Proposed Solution

### 2016-01-28 design.tex
need empty relations!

>>>>

Different classes of rules that we consider are represented as types.
These types tend to be pairs of values with a relation.
For instance, an integer relation rule is a pair of keywords with a formula that the pairs must satisfy.
It is important that the relation has some empty value, to state that there is no relation between the values.
This will prevent \app from trying to relearn rules when they have been eliminated from the set.
